Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-11 write-ups/PLDI/paper.tex

\ADComment{TODO: explain why we have thread 0 transmit its state, and transmitting only annotated variables.}

\ADComment{Something old to maybe work in:}

The programmer is responsible for keeping at least one workgroup alive.  In particular, if all workgroups execute $\offerkill$, the scheduler is at liberty to destroy all workgroups, causing the cooperative kernel to exit.  This can be guarded against by wrapping each $\offerkill$ call in a conditional statement:

\lstset{basicstyle=\tt,numbers=none}
\begin{lstlisting}
  if($\getgroupid{0}$ != 0) $\offerkill$();
\end{lstlisting}
\lstset{basicstyle=\scriptsize\tt,numbers=left}

We could, alternatively, have formulated the semantics of $\offerkill$
so that workgroup 0 is never killed.  However, there might be a use
case for a cooperative kernel reaching a point where it would be
acceptable for the kernel to exit, although desirable for some
remaining computation to be performed if competing workloads allow it.

>>>>

Recall from the semantics of $\offerfork$ that newly forked workgroups
inherit the variable valuation associated with thread 0 of the forking
workgroup, but only for $\transmit$-annotated variables.  Alternative
choices here would be to have forked workgroups inherit values for
\emph{all} variables from the forking workgroup, and to have thread
$i$ in the forking workgroup provide the valuation for thread $i$ in
each spawned workgroup, rather than having thread 0 transmit the
valuation to all new threads.

\ADComment{TODO: justify our choice: uniform variables and efficiency.}
